---
title: "Final Assignment"
author: "Author: Rebecca Meador"
date: "`r format(Sys.Date(), '%A, %B, %d, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Document Summary**

This is my final assignment for the Coursera course titled, "Reproducible Templates for Analysis and Dissemination." This document will list some of the skills I learned in this course.  It will also include several elements that I learned about using in an **RMarkdown document** such as a bulleted list, a  plot, a table, and a document theme.  

### **What I learned in this course**

In this course, I learned the following:

* How to create an RMarkdown document
* How to knit my document to the following formats:
    + HTML
    + Docx
    + PDF
* How to create a website using RStudio
* How to publish my new website using Rpubs

I also learned how to insert a plot into my document using data from a built-in data set:

### **Plot of Pressure Dataset**

```{r pressure, echo=FALSE}
plot(pressure)
```

Additionally, I learned how to insert a table into my document using data from a built-in data set:

### **Table Using the Cars dataset**

```{r cars, echo=FALSE}
head(cars,6)
```

## **Conclusion**

Having never used R or RStudio before, everything in this course was new to me.  I learned a great deal about how to use RStudio to make modular templates that are easy to create, use, and share. I also learned how to easily disseminate my work on the web.



